### 2012-07-29 Doc/VRIPHYS2012/vriphys2012.tex
comments and some update
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@434 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

% TODO
The main contributions of the paper are following:
\begin{itemize}
    % not really novel, similar model already in Ubach2010
    %\item shell element based on Bézier triangles
    \item Our element solves the problems of the element presented by Comas
        \cite{Comas2010c}: it is continuous on the element boundary and has
        all rotational degrees of freedom.

@@

In this subsection we propose an element featuring interpolation with high degree of flexibility while still maintaining low number of degrees of freedom.
We introduce a new way of building the interpolation by using two stages:
\begin{enumerate}
    \item A B\'ezier interpolation with cubic polynomial functions is defined on a triangle.
    \item A kinematic relation between nodes (6DOFs) defined at the vertices and the control points of the B\'ezier triangle.
\end{enumerate}

@@

For the central point we again apply interpolation of \eqref{eq-central} which is kind of skinning function:

@@

@@

@@

\noindent
and variation of central point $\delta P_{10}$:

@@

\begin{equation}\label{bez-delta}
    \begin{split}
        \delta T = &   (n_1 + n_4 + n_5 + \frac{1}{3} n_{10})  \delta \mathbf{x}_1 + \\
                   & + (n_2 + n_6 + n_7 + \frac{1}{3} n_{10})  \delta \mathbf{x}_2 + \\
                   & + (n_3 + n_8 + n_9 + \frac{1}{3} n_{10})  \delta \mathbf{x}_3 + \\
                   & + \sum_{j=4}^9 P_{i-j} \times \delta \mathbf{\theta}_j + \\
                   & + n_{10} \frac{1}{3} \sum_{j=4}^9 P_{i-j} \times \mathbf{\theta}_i
    \end{split}
\end{equation}

@@

\section{...} % {{{

@@

@@

% We cannot show results for simple plane in bending because the solution
% seems to converge to wrong value (but it converges! :)). Thus showing
% results for plain membrane deformations doesn't make sense (it would be
% inconsistent).

>>>>

% TODO
The main contributions of the paper are following \CD{- Tomas, you need to write sentences here -}

\begin{itemize}
    % not really novel, similar model already in Ubach2010
    %\item shell element based on Bézier triangles
    \item Our element solves the problems of the element presented by Comas
        \cite{Comas2010c}: it is continuous on the element boundary and has
        all rotational degrees of freedom.

@@

In this subsection we propose an element featuring interpolation with high degree of flexibility while still maintaining low number of degrees of freedom.
We introduce a new way of building the interpolation by using two stages 
\CD{ - Need a figure here - }:
\begin{enumerate}
    \item A B\'ezier interpolation with cubic polynomial functions is defined on a triangle.
    \item A kinematic relation between nodes (6DOFs) defined at the vertices and the control points of the B\'ezier triangle.
\end{enumerate}

@@

For the central point we again apply interpolation of \eqref{eq-central} which is kind of skinning function \CD{Why so complicated ?
You can compute  some rules to chose the first location of point $P_{10}$ (i.e. to compute $P_{i-10}$) but then use something more simple for the kinematics}:

@@

\CD{I would have put (but that is maybe the same result...)}

\begin{equation}\label{eq-central}
    \begin{split}
        P_{10} =  \frac{1}{3}\left( \sum_{i=1}^3 \mathbf{x}_i + R(\theta_i) \overline{P_{i-10}} \right)
    \end{split}
\end{equation}

@@

\CD{and it could be possible to write down (and this is helpful for the formulation of the spacial derivative):}
\begin{equation}\label{global-transform}
    \begin{split}
 T(\xi_1,\xi_2, \xi_3) = \sum_{i=1}^{10} n_i(\xi_1,\xi_2, \xi_3)P_i = \\
 	\sum_{i=1}^{3} n_i(\xi_1,\xi_2, \xi_3) \mathbf{x}_i +  \sum_{j=4}^9 n_j (\xi_1,\xi_2, \xi_3)( \mathbf{x}_i +  R(\theta_i) \overline{P_{i-j}}) + \\  \frac{n_{10}(\xi_1,\xi_2, \xi_3)}{3}\left( \sum_{i=1}^3 \mathbf{x}_i + R(\theta_i) \overline{P_{i-10}} \right) 
    \end{split}
\end{equation}

@@

\noindent
and variation of central point $\delta P_{10}$ \CD{ this formulation would be simplified...} :

@@

\begin{equation}\label{bez-delta}
    \begin{split}
        \delta T = &   (n_1 + n_4 + n_5 + \frac{1}{3} n_{10})  \delta \mathbf{x}_1 + \\
                   & + (n_2 + n_6 + n_7 + \frac{1}{3} n_{10})  \delta \mathbf{x}_2 + \\
                   & + (n_3 + n_8 + n_9 + \frac{1}{3} n_{10})  \delta \mathbf{x}_3 + \\
                   & + \sum_{j=4}^9 P_{i-j} \times \delta \mathbf{\theta}_j + \\
                   & + n_{10} \frac{1}{3} \sum_{j=4}^9 P_{i-j} \times \delta \mathbf{\theta}_i 
    \end{split}
\end{equation}

@@

%%%%%%%%%%%%%%%%%%%%%%%%% SECTION 3 %%%%%%%%%%%%%%%

\section{Finite element formulation} % {{{

In the previous section we present an interpolation based on cubic B\'ezier triangles and a kinematic link between the control points and the element 6DoF Nodes.
In this section we show how this interpolation can be used to compute a finite element formulation of the shell equations.

\subsection{Computation of the strain tensor}

We define a local system of coordinates $(x,y,z)$ in which the axis z is oriented along the thickness of the element. (\CD{TODO: figure}) 
For the shell formulation, there is no need to compute the derivatives along axis $z$.

The 2D tensor of deformation can be defined as a $2\times2$ matrix in which the components $k=\{x,y\}$ and $l=\{x,y\}$are:
\begin{equation}
F_{kl} = \frac{\delta T^k}{\delta l}   
\end{equation}

@@

%%%%%%%%%%%%%%%%%%%%%%%%% SECTION 4 %%%%%%%%%%%%%%%

@@

% We cannot show results for simple plane in bending because the solution
% seems to converge to wrong value (but it converges! :)). Thus showing
% results for plain membrane deformations doesn't make sense (it would be
% inconsistent).
  \CD{ - On this section,  we can maybe add some results from the CBM paper you did with Stephan especially  the figure 9 that illustrates the 3d contribution we list in the intro: i.e. Mapping of high resolution mesh on the curved surface of the shell.}
